Methods

### 2019-01-22 Methods.Rmd
some_changes

Now we select only the sites occuring along the west coast. Thereafter, I include all the sites which had a time series of 10years or greater. This yield a 2 rows of data for Paternoster. I removed the row of data obtained by the DEA, thus ending up with all of the data being obtained from SAWS in this dataset. I then exclude the sites that do not fall within the upwelling cell. Once those sites were removed, we have a total of 9 sites. These are: Port Nolloth, Hondeklip baai, Doring baai, Lamberts Bay, Elands Bay, St Helena Bay, Paternoster, Saldanna and Yzerfontein.

@@

SACTN_daily_temps <- SACTN_daily_v4.2 %>% 
  left_join(site_list[,c(4,13)], by = "index") %>% 
  filter(index %in% upwelling_sites$index)

# save(SACTN_daily_temps, file = "SACTN_daily_temps.RData")

SACTN_daily_temps_indexsplit <- SACTN_daily_temps %>% 
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>% 
  dplyr::rename(insitu_temp = temp)

# save(SACTN_daily_temps_indexsplit, file = "Data/SACTN_daily_temps_indexsplit.RData")
```

@@

SACTN_3yr <- SACTN_split %>% 
  filter(year(date) %in% seq(1998, 1999, 2000))
```

```{r}
ggplot(data = SACTN_3yr , aes(x = date, y = insitu_temp)) +
  geom_hline(aes(yintercept = mean(insitu_temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 4) +
  theme_bw()
```

@@

```{r}
MUR_Doringbaai <- read_csv("Data/MUR_nearest5pixels/MUR_Doringbaai_SST_timeseries_5nearest.csv")
MUR_Elands_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Elands Bay_SST_timeseries_5nearest.csv")
MUR_Hondeklipbaai <- read_csv("Data/MUR_nearest5pixels/MUR_Hondeklipbaai_SST_timeseries_5nearest.csv")
MUR_Lamberts_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Paternoster <- read_csv("Data/MUR_nearest5pixels/MUR_Paternoster_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data/MUR_nearest5pixels/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_St_Helena_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_St Helena Bay_SST_timeseries_5nearest.csv")
MUR_Yzerfontein <- read_csv("Data/MUR_nearest5pixels/MUR_Yzerfontein_SST_timeseries_5nearest.csv")

MUR_SST <- rbind(MUR_Doringbaai,MUR_Elands_Bay, MUR_Hondeklipbaai,MUR_Lamberts_Bay,MUR_Yzerfontein,
                 MUR_Paternoster, MUR_Port_Nolloth,MUR_Saldanha_Bay, MUR_St_Helena_Bay) %>%
  dplyr::rename(site = station)

@@

match_func <- function(df){
  match <- SACTN_split  %>%  
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

@@

```{r}
match_plot <- function(df){
  plot1 <- df %>% 
ggplot(aes(x = date, y = temp)) +
  geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 4) +
  theme_bw()
  return(plot1)
}

MUR_plot <- match_plot(df = MUR_SST)
```

################################

-  Need to plot a line graph with all SST dat and the insitu data on one graph

################################

Here I load the AVHRR CSV dataset.

```{r}
# AVHRR <- read_csv("data/csvavhrr-only-v2-19810901-20180630.csv")

@@

```{r}
load("~/Documents/MastersProject/Data/combined_OISST_sites.RData")
```

## Matching the Insitu data with the OISST SST data
- Here there are many NA values because the OISST have many values collected per day where as the insitu temp only has 1

@@

>>>>

Now we select only the sites occuring along the west coast. Thereafter, I include all the sites which had a time series of 10years or greater. This yield a 2 rows of data for Paternoster. I removed the row of data obtained by the DEA, thus ending up with all of the data being obtained from SAWS in this dataset. I then exclude the sites that do not fall within the upwelling cell. Once those sites were removed, we have a total of 4 sites. These are: Port Nolloth, Lamberts Bay, Saldanna and Yzerfontein.

@@

# Here I find a time series with the data occuring in the most recent years
upwelling_sites <- upwelling_sites[c(-2, -3, -5, -6, -8),] 
# save(upwelling_sites, file = "Data/upwelling_sites.RData")

SACTN_daily_temps <- SACTN_daily_v4.2 %>% 
  left_join(site_list[,c(4,13)], by = "index") %>% 
  filter(index %in% upwelling_sites$index)
# save(SACTN_daily_temps, file = "SACTN_daily_temps.RData")

SACTN_daily_temps_indexsplit <- SACTN_daily_temps %>% 
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>% 
  dplyr::rename(insitu_temp = temp)
# save(SACTN_daily_temps_indexsplit, file = "Data/SACTN_daily_temps_indexsplit.RData")
```

@@

SACTN_3yr <- SACTN_split %>% 
  filter(year(date) %in% seq(2015, 2016))
```

```{r}
ggplot(data = SACTN_3yr , aes(x = date, y = insitu_temp)) +
  geom_hline(aes(yintercept = mean(insitu_temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 2) +
  theme_bw()
```

@@

```{r}
MUR_Lamberts_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data/MUR_nearest5pixels/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data/MUR_nearest5pixels/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_Yzerfontein <- read_csv("Data/MUR_nearest5pixels/MUR_Yzerfontein_SST_timeseries_5nearest.csv")

MUR_SST <- rbind(MUR_Lamberts_Bay,MUR_Yzerfontein, MUR_Port_Nolloth,MUR_Saldanha_Bay) %>%
  dplyr::rename(site = station)

@@

match_func <- function(df){
  match <- SACTN_3yr  %>%  
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

@@

```{r}
match_plot <- function(df){
  plot1 <- df %>% 
ggplot(aes(x = date, y = temp)) +
  geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 2) +
  theme_bw()
  return(plot1)
}

MUR_plot <- match_plot(df = insitu_MUR)
```

Here I load the AVHRR OISST CSV dataset. 
```{r}
# AVHRR <- read_csv("data/csvavhrr-only-v2-19810901-20180630.csv")

@@

```{r}
# load("~/Documents/MastersProject/Data/combined_OISST_sites.RData")
```

## Matching the Insitu data with the OISST SST data

@@

##
